Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Starting Results

% I don't think "collections" should be nodes too. They are simply
% attributes for an individual - JJ
% They are nodes, I added the reason above. - Mario
For instance a relational database can be used for the implementation of a
user profile and authentication module. Also a copy or cache of the population 
could be kept in a key-value store in memory for performance reasons. 
Nevertheless, the model can give important insights of the behavior of the 
system.   % So what we have done here is this and that because... - JJ

\section{Case Study}
\label{sec:experiments}

@@

Only the ``Start a session'' and ``Explore collections of other friends'' actions 
are not reflected in the graph model since they are stored instead in the PostgreSQL relational
database system. % because... - JJ

Two scores are used to determine the weight of a user's preference:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100. 
% More details needed? Is done by a Fuzzy Inference System but I think
% the description would take to much space.
% Better a small description than nothing. If you need space, some
% sections above are maybe a bit too verbose - JJ

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users where invited to the system by him.   
\end{itemize}

@@

The link used in the call for participation
was shortened Google URL, that provides metadata and analytics for the
users that click on it. 
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.    
%Isn't this anonymous? - JJ

@@

% Time
\subsection{Results}
\label{sec:results}

>>>>

% I don't think "collections" should be nodes too. They are simply
% attributes for an individual - JJ
% They are nodes, I added the reason above. - Mario
For instance a relational database was used for the implementation of a 
basic user profile and authentication module. Also the active population 
was kept in a key-value store in memory for performance reasons.  
Nevertheless, having a multi-model implementation can give important 
insights of the behavior of the system. This architecture was validated
by a case study, requiring the interaction of all of the components.        
 % So what we have done here is this and that because... - JJ
 % Changed the paragraph. - Mario 
% refinement
\section{Case Study}
\label{sec:experiments}

@@

Only the ``Start a session'' and ``Explore collections of other friends'' actions 
are not reflected in the graph model since they are stored instead in the PostgreSQL relational
database system. This is because user sessions and authentication, as well as basic
web requests, are handled directly by the django web framework \cite{garcia2013evospace}.  
     % because... - JJ
     % done - Mario

Two scores are used to determine the weight of a user's preference:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100. It is assumed for this case, that once a user
reaches a 100 actions, it has enough experience on using the application.   
% More details needed? Is done by a Fuzzy Inference System but I think
% the description would take to much space.
% Better a small description than nothing. If you need space, some
% sections above are maybe a bit too verbose - JJ
% I checked and this is not a fuzzy value. Explained any way. - Mario

\item Participation. This value is simply the degree of the user node 
in the graph. This measure considers the number of users he knows,
collections and phenotypes rated.    
\end{itemize}

@@

The link used in the call for participation
was shortened Google URL, that provides metadata and analytics for the
users that click on it. 
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.    
%Isn't this anonymous? - JJ
% like in double blind? I think so, that is why no link is given in the table. - Mario

@@

\subsection{Results}
\label{sec:results}
